Synthesis of Linear Functional Programs

### 2021-07-15 article/article.tex
retoques

% General motivation?
Program synthesis is an automated or semi-automated process of deriving a
program, i.e.~generating code, from a high-level specification. Synthesis can be
seen as a means to improve a programmer's productivity and program correctness
(e.g. through suggestion and autocompletion).
%
Specifications can take many forms: natural language~\cite{chen2021evaluating},
examples~\cite{DBLP:conf/popl/FrankleOWZ16}, polymorphic refinement
types~\cite{DBLP:conf/pldi/PolikarpovaKS16}, graded linear
types~\cite{DBLP:conf/lopstr/HughesO20}, \emph{etc.}, but, regardless the kind of
specification, program synthetisers have to deal with two main inherent sources
of complexity -- searching over a vast space of (potentially) valid programs,
and interpreting user intent.

>>>>

% General motivation?
Program synthesis is an automated or semi-automated process of deriving a
program, i.e.~generating code, from a high-level specification. Synthesis can be
seen as a means to improve programmer productivity and program correctness
(e.g. through suggestion and autocompletion).
%
Specifications can take many forms such as natural
language~\cite{chen2021evaluating},
examples~\cite{DBLP:conf/popl/FrankleOWZ16} or rich types such as
polymorphic refinement types~\cite{DBLP:conf/pldi/PolikarpovaKS16} or
graded types~\cite{DBLP:conf/lopstr/HughesO20}. Regardless of the kind
of specification, program synthesizers have to deal with two main
inherent sources of complexity -- searching over a vast space of
(potentially) valid programs, and interpreting user intent.
